% Source: CPTR 280 Computer Organization and Assembly Language Fall 2023
% File: "07 Memory (key).pdf"
% Author: James Foster, pogil@jgfoster.net

% comment out for student version
% \ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Activity 7: Memory}
\author{James Foster}
\newcommand{\activityeditor}{James Foster}
\newcommand{\activitysource}{\url{pogil@jgfoster.net}}
\date{Fall 2023}

\input{../../cspogil.sty}
\usepackage{graphicx}
\usepackage{tabularx}

\begin{document}

  \begin{center}
    \maketitle
    \rolenames
  \end{center}

  \keyquestions{
  \item Model 1, Question \#10
  \item Model 2, Question \#14
  \item Model 3, Question \#21
  }

  \newpage
  \maketitle

  In previous activities, we explored combinational logic circuits where outputs depend only on current inputs.
  However, computers need to remember information—they need memory. This activity introduces sequential logic circuits,
  where outputs depend on both current inputs and previous states. We'll build up from the simplest memory element (a flip-flop that stores one bit)
  to more complex circuits that can store and retrieve multiple bits using addresses. Understanding how memory works at the hardware level is fundamental to
  grasping how computers store programs, data, and maintain state during execution.
  
  \guides{
    \item Students will be able to explain how a flip-flop maintains state using feedback.
    \item Students will be able to distinguish between level-triggered and edge-triggered D flip-flops.
    \item Students will be able to describe how addressable memory uses select lines to read or write specific memory locations.
    \item Students will be able to trace the flow of data through memory circuits.
   }{
    \item Analyzing circuit diagrams to understand data storage and retrieval.
    \item Comparing different types of flip-flops and their timing characteristics.
    \item Collaborating to trace signals through sequential circuits and build understanding collectively.
   }{
    No additional notes
   }{
    \item \url{https://www.codehiddenlanguage.com/}
   }

  \input{feedback.tex}
  \newpage
  \input{flip_flop.tex}
  \newpage
  \input{level_trigger_d_flip_flop.tex}
  \newpage
  \input{edge_triggered_d_flip_flop.tex}
  \newpage
  \input{addressable_memory.tex}

\end{document}