\model{One Dimensional Arrays}
  \begin{center}
    \begin{minipage}{6.5in}
      \begin{cpplst}
string homeworkNames[5] = {"Variables","If-Else","Loops","Vectors","Arrays"};
int pointsPossible[5] = {25, 35, 15, 20, 30};
int numStudents = 40;

for (int i=0; i<5; i++) {
  cout << homeworkNames[i] << ": " << pointsPossible[i] << endl;
}
cout << pointsPossible[5] << endl;
      \end{cpplst}
    \end{minipage}
  \end{center}  
  
  {\it\large Refer to Model 1 above as your team develops consensus answers
    to the questions below.}

  \quest{15 min}

  \Q Like vectors, arrays can be used to store a list of elements
    of the same type.  Answer the following questions about the arrays
    in the model above.
    \begin{enumerate}
      \itemsep 10pt
      \item What are the names of the two arrays used in the model?
        \hfill \ans[2.25in]{\tt homeworkNames, pointsPossible}

      \item What are the types of the two arrays in the model?
        \hfill \ans[2.25in]{\cpp{string} and \cpp{int}}

      \item What are the sizes of the two arrays in the model?
        \hfill \ans[2.25in]{18 and 5}

      \item What word describes the relationship between the arrays?
        \hfill \ans[2.25in]{parallel}

      \item How would you access the last element of {\tt homeworkNames}?
        \hfill \ans[2.25in]{\cpp{homeworkNames[4]}}
    \end{enumerate}       
    
  \vskip -20pt
    
  \Q Based on the model, describe how the following symbols are
    used with arrays.
    \begin{enumerate}
      \item The curly braces, \cpp{\{ \}.}
        \begin{answer}[0.5in]
          They are used to initialize the contents of the array when
          declaring it.
        \end{answer}

      \item The square brackets, \cpp{\[ \].}  Give two different ways they are used.
        \begin{answer}[0.75in]
          They are used to specify the size of the array when
          declaring it and to access an element in the array.
        \end{answer}
    \end{enumerate}

  \Q Without running it, predict what the code from this model
    will print out.
    \begin{answer}[0.75in]
      \small\tt\hspace{10pt}
      \scriptsize
      \begin{minipage}{4in}
        Variables: 25\\
        If-Else: 35\\
        Loops: 15\\
        Vectors: 20\\
        Arrays: 30\\
        <random integer>
      \end{minipage}
    \end{answer}
    
  \Q This code can be found in {\tt activity16a.cpp}.  Run it and
    explain what you see.
    \begin{answer}[0.5in]
      It prints out the first 5 elements of each array, but the
      value of \cpp{pointsPossible[5]} is undefined
      since the index 5 is past the array bounds of 0-4.
    \end{answer}
    
  \Q What happens if you change line 8 to \cpp{cout << pointsPossible}?
    \begin{answer}[0.5in]
      You get a memory address, such as {\tt 0x7ffd360a1840}.
    \end{answer}

  \vskip -10pt
          
  \Q Suppose that you were asked to rewrite this program to use
    vectors instead of arrays.\key\\[-15pt]
    \begin{enumerate}
      \item How would you change lines 1 and 2 to
        declare vectors instead of arrays?
        \begin{answer}[0.75in]
          \fs
          \begin{minipage}{4.5in}
            \begin{cpplst}
vector<string> homeworkNames(5) = {"Variables","If-Else","Loops","Vectors","Arrays"};
vector<int> pointsPossible(5) = {25, 35, 15, 20, 30};
            \end{cpplst}
          \end{minipage}        
        \end{answer}
          
      \item How would you change line 6 to print out the vector values?
        \begin{answer}[0.75in]
          \begin{minipage}{4.5in}
            \begin{cpplst}
cout << homeworkNames.at(i) << ": " << pointsPossible.at(i) << endl;
            \end{cpplst}
          \end{minipage}     
        \end{answer}
          
      \item Suppose line 8 was changed to \cpp{cout << pointsPossible.at(5) << endl;}.  What would happen when the
        program runs that command?
        \begin{answer}[0.5in]
          The program would crash with an out-of-range error.
        \end{answer}
    \end{enumerate}

  \newpage
      
  \Q The code below is designed to collect 100 names and then
    print out a random one.  It is built using vectors.  Rewrite it
    using arrays.
    
    \begin{tabular}{p{3.5in}p{2.9in}}
      \begin{minipage}{3.5in}
        \small
        \begin{cpplst}
vector<string> names;
string tmpName;
for (int i = 0; i < 100; i++) {
  cout << "Name " << (i + 1) << ": ";
  cin >> tmpName;
  names.push_back(tmpNames);
}
cout << names.at(rand() % 100) << endl;
        \end{cpplst}
      \end{minipage}
      &
      \begin{minipage}{2.9in}
        \fs
        \begin{answer}[2in]
        \scriptsize
        \begin{cpplst}
string names[100];
for (int i = 0; i < 100; i++) {
  cout << "Name " << (i + 1) << ": ";
  cin >> names[i];
}
cout << names[rand() % 101] << endl;
        \end{cpplst}
          
        \end{answer}
      \end{minipage}
    \end{tabular}