{\bf\large Model 1: A C++ Program} \\
  \begin{center}
    \begin{minipage}{3.5in}
      \begin{minted}[
        frame=lines,
        framesep=2mm,
        bgcolor=gray!15,
        baselinestretch=1.2,
        linenos
      ]{cpp}
#include <iostream>
using namespace std;

int main() {
  cout << "Go!$\backslash$n";
}      
      \end{minted}
    \end{minipage}
  \end{center}
  \par\vskip 10pt
  
  {\it\large Refer to Model 1 above as your group develops consensus answers
    to the questions below.}
    \par\vskip 10pt
    
  \begin{enumerate}
    \itemsep 20pt
    
    \item The file {\tt activity01a.cpp} contains this C++ program. Run it and determine what it does.
      \begin{solution}[0.5in]
        It prints out the text {\it Go!}
      \end{solution}
      
    \item Replace line 5 with each of the following.  What is produced?  Indicate if
      there is a problem.\par\vskip 20pt      
      \begin{enumerate}[(a)]
        \itemsep 10pt
        \item {\tt cout << "Hello, my name is Jon";} \hfill
          \fillin[It prints {\it Hello, my name is Jon}][3in]
        \item {\tt cout << Hello, my name is Jon;} \hfill
          \fillin[It produces an error][3in]
        \item {\tt cout << "Hello,$\backslash$nmy name is Jon";} \hfill
          \fillin[Same as (a), but with a line break][3in]
      \end{enumerate}
      
\newpage      
      
    \item A {\it string literal} is a sequence of characters surrounded by double
      quotation marks (" ").  Use this term to describe the difference between part (a)
      and part (b) above.
      \begin{solution}[1in]
        Part (a) prints out the string literal "Hello, my name is Jon" while in part (b)
        the lack of quotation marks confuses the compiler.
      \end{solution}
      
    \item What caused the different output format for statements (a) and (c) in question 2?
      \begin{solution}[1in]
        The $\backslash$n in part (c) caused a line break instead of the space we
        got in part (a)
      \end{solution}

    \item What do you think the following C++ statements output?\key\\[-2.5mm]
      \par\vskip 20pt
      \begin{enumerate}[(a)]
        \itemsep 10pt
        \item {\tt cout << 2+5;} \hfill
          \fillin[It prints {\it 7}][2.5in]
        \item {\tt cout << 2*5;} \hfill
          \fillin[It prints {\it 10}][2.5in]
        \item {\tt cout << "2+5";} \hfill
          \fillin[It prints {\it 2+5}][2.5in]
        \item {\tt cout << "Age:" << 20;} \hfill
          \fillin[It prints {\it Age: 20}][2.5in]
      \end{enumerate}
              
    \item With reference to the output for each statement in question 5,
      \begin{enumerate}[(a)]
        \itemsep 10pt
        \item What is the difference in the output for statements (a) and (c)?
          \begin{solution}[1in]
            Statement (a) prints computes the value of 2+5 and prints it out, while
            statement (c) prints out the literal characters {\it 2+5}.
          \end{solution}          
        \item What caused the difference?
          \begin{solution}[0.5in]
            The quotation marks around the {\it 2+5} in statement (c) made it into a
            string literal.
          \end{solution}
        \item Which statement(s) contained a {\it string literal}? Explain. \hfill
          \fillin[Statement (c), it has quotes around it][2.5in]
        \item What does the extra {\tt <<} do in part (d) of question 4?  How does it
          affect the spacing of the output?
          \begin{solution}[1in]
            \par
            It outputs the second item right after the first, resulting in {\it Age:} and
            {\it 20} being put together.\par
            It does not add any extra space between the two items.
          \end{solution}
      \end{enumerate}
      
  \end{enumerate}

  \newpage
