{\bf\large Model 1: A C++ Main Function} \\[-15pt]
  \begin{center}
    \begin{minipage}{4.25in}
      \small
      \begin{minted}[
        frame=lines,
        framesep=2mm,
        bgcolor=gray!15,
        baselinestretch=1,
        linenos,
        firstnumber=8
      ]{cpp}
int main() {
  ofstream fout;
  fout.open("studentInfo.txt", ofstream::app);

  string firstName = input("Enter first name: ");
  string lastName = input("Enter last name: ");
  string studentID = input("Enter student ID: ");

  fout << "Name: " << firstName << " " << lastName << endl;
  fout << "Student ID: " << studentID << endl;
  fout << endl;
  fout.close();

  cout << "Done! Data is saved in: studentInfo.txt" << endl;  
}        
      \end{minted}
    \end{minipage}
  \end{center}  
  
  {\it\large Refer to Model 1 above as your team develops consensus answers
    to the questions below.}
    \par\vskip 10pt
    
  \begin{enumerate}
    \itemsep 20pt
 
    \item This code can be found in {\tt activity18a.cpp}.  Run it and
      record what output appears on the screen.
      \ifprintanswers\vskip -20pt\null\fi
      \begin{solution}[1in]
        The program says:
        \begin{itemize}
          \itemsep 0pt
          \item Enter first name:
          \item Enter last name:
          \item Enter student ID:
          \item Done! Data is saved in: studentInfo.txt
        \end{itemize}
      \end{solution}
      \ifprintanswers\vskip -30pt\null\fi

    \item Locate the file {\tt studentInfo.txt} and examine its contents.
      \par\vskip 15pt
      
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item What is in this file?
          \hfill \fillin[the student info we entered][3in]
        \item Did this file exist before the program ran?
          \hfill \fillin[no, it was created by the program][3in]
        \item On which line of code was the file created?
          \hfill \fillin[line 10, by the {\tt .open()} command][3in]
        \item Which lines generated the file contents?
          \hfill \fillin[lines 16 through 18][3in]
        \item Why wasn't the message on line 21 in the file?
          \hfill \fillin[because it was sent to {\tt cout} not {\tt fout}][3in]
      \end{enumerate}
    
\newpage

    \item Run the program again using different input.  Then open the
      {\tt studentInfo.txt} file.  What is in the file?  Is the data
      from the first time you ran it still there?
      \begin{solution}[0.5in]
        The file has original student's info as well as the
        new one from our second execution.
      \end{solution}
      \ifprintanswers\vskip -40pt\else\vskip -20pt\fi\null

    \item Remove the {\tt ofstream::app} argument in the {\tt .open()}
      function call on line 10 and run the\key\\[-2.5mm] program again with different input.
      \par\vskip 15pt
      
      \begin{enumerate}[(a)]
        \item What happened to the contents of {\tt studentInfo.txt}?
          \begin{solution}[0.5in]
            The contents of {\tt studentInfo.txt} were replaced with the
            new input.
          \end{solution}
        \item What did the {\tt ofstream::app} argument do?
          \begin{solution}[0.5in]
            The argument made the program {\it append} to the
            file instead of {\it overwrite} the file.
          \end{solution}
      \end{enumerate}
            
      
    \item You should have observed that lines 16-18 send output to the
      the file {\tt studentInfo.txt}.  How does C++ know to send the
      output to that file?
      \begin{solution}[0.5in]
        The {\tt fout} variable was opened with that file name.
      \end{solution}
      
    \item Rewrite the program so the user can keep entering names
      until they type in {\tt DONE} for the first name.
      \begin{solution}[1.75in]
        Wrap lines 12-18 in a {\tt do-while} loop with condition 
        \mintinline{cpp}|firstName != "DONE"|.
      \end{solution}