\model{Redirecting Output to a File}
  \begin{center}
    \begin{tabular}{p{2.8in}p{0.1in}p{2.7in}}
      \begin{minipage}{2.8in}
        \small
        \begin{cpplst}    
for (int i = 1; i <= 5; i++) {
  cout << "Number: " << i << endl;
}
cerr << "Done!" << endl;
        \end{cpplst}
      \end{minipage}
      & &
      \begin{minipage}{2.7in}
        \centering\tt terminal commands\vskip -5pt
        \begin{verbatim}
g++ activity18c.cpp -o test.o
./test.o > output.txt 2> error.txt
        \end{verbatim}    
      \end{minipage}
    \end{tabular} 
  \end{center}  
    
  {\it\large Refer to Model 2 above as your team develops consensus answers
    to the questions below.}
    
  \quest{15 min}

  \Q The file {\tt activity18b.cpp} contains the code shown on the left-hand side of the
    model.  Run this program as you normally would and describe its
    output.
    \begin{answer}[0.75in]
      The program outputs ``Number: 1'' through ``Number: 5'' and
      then outputs ``Done!''.
    \end{answer}
    
  \Q Now open a terminal in this same folder (right click on the folder name and pick {\it
    Open in Terminal}) and type in the commands shown in the model, pressing {\tt Enter} after each line.
    \begin{enumerate}
      \itemsep 10pt
      \item What is output to the screen? \hfill\ans[2.5in]{nothing}
      \item What new files now appear in the folder?
        \hfill\ans[2.5in]{{\tt output.txt} and {\tt error.txt}}

      \item Which file contains the output from {\tt cout}?
        \hfill\ans[2.5in]{{\tt output.txt}}

      \item Which file contains the output from {\tt cerr}?
        \hfill\ans[2.5in]{{\tt error.txt}}
    \end{enumerate}

  \Q Recall that the command {\tt ./program.o < input.txt} {\it
    redirects} the contents of the {\tt input.txt} file to the
    program as if it were entered from the keyboard.  The command
    above redirects the program output to various files.
    \begin{enumerate}
      \itemsep 15pt
      \item What part of the second terminal command redirects the
        output set to {\tt cout} to a file?
        \begin{answer}[0.5in]
          The part {\tt > output.txt}
        \end{answer}

      \item What par tof the command redirects the output sent to
        {\tt cerr} to a file?
        \begin{answer}[0.5in]
          The part {\tt 2> error.txt}
        \end{answer}
    \end{enumerate}
          
  \Q Pick a previous homework assignment that produces output.
    Open a terminal\key\\[-2.5mm] in that folder, compile the program, and save
    the output to a file.  Recall that we have not used {\tt cerr} 
    previously, so you only need to direct the output from {\tt cout}.
    What command did you use?
    \begin{answer}[0.5in]
      {\tt ./program.o > output.txt}
    \end{answer}