\model{Reorder Function Analysis}

  \texttt{Reorder} is a method that sorts two array elements.

  \begin{cpplst}
void reorder(int array[], int i, int j) {
    if (array[i] > array[j]) {
        int temp = array[i];
        array[i] = array[j];
        array[j] = temp;
    }
}
  \end{cpplst}

  \par\vskip 10pt

  {\it\large Refer to Model 1 above as your team develops consensus answers
    to the questions below.}

  \quest{15 min}

  \Q Suppose an array \texttt{a} contains the values \texttt{\{6, 11, 9, 13\}}.
    List the contents of \texttt{a} after the method call \texttt{reorder(a, 1, 2)}
    \begin{answer}[1.25in]
      The contents of \texttt{a} are \texttt{\{6, 9, 11, 13\}}.
    \end{answer}

  \Q Suppose we define an \emph{operation} as an assignment statement,
    arithmetic operation, or comparison.  How many operations does
    the method execute when \texttt{reorder(a, 1, 2)} is called?
    \begin{answer}[1.25in]
      The method executes 4 operations.
    \end{answer}

  \Q How many operations does the method execute when \texttt{reorder(a, 0, 1)} is called?
    \begin{answer}[1.25in]
      The method executes 3 operations.
    \end{answer}

  \Q Suppose an array \texttt{b} contains the values \texttt{\{2, 6, 13, 8, 3\}}.  How
    many operations does the method execute when \texttt{reorder(b, 3, 4)} is
    called?
    \begin{answer}[1in]
      The method executes 4 operations.
    \end{answer}

  \Q How many operations does the method execute when \texttt{reorder(b, 1, 2)} is called?
    \begin{answer}[1in]
      The method executes 3 operations.
    \end{answer}

  \Q Is there an upper bound on the number of operations that \texttt{reroder} can
    execute? Why or why not?
    \begin{answer}[1in]
      Yes. The upper bound is 4 operations because that is the maximum number of
      operations that can be executed in any case.
    \end{answer}

  \Q Does the number of operations the method executes depend on the size of its input\key\\[-2.5mm]
    (\emph{i.e.}, the number of elements in the input)? Why or why not?
    \begin{answer}[1in]
      No. The number of operations does not depend on the size of the input
      because the method only compares and possibly swaps two elements, regardless
      of how many elements are in the array.
    \end{answer}

  \Q We say that the \texttt{reorder} method executes in \emph{constant} time.
    Another way to say this is that the method is $\Theta(1)$.  Complete the
    following sentence: \\
    \ \\
    A method is $\Theta(1)$ (or executes in constant time)
    if...
    \begin{answer}[1in]
      ...the number of operations it executes does not depend on the size of its input.
    \end{answer}