\model{A Circle Class}
  \begin{center}
    \begin{tabular}{c c c}
      \begin{minipage}{2.5in}
        \begin{tabular}{|l|}
          \hline
          \rowcolor{orange!20}\multicolumn{1}{|c|}{\bf Point}\\
          \hline
          \rowcolor{white} \tt -xPos: double\\
          \rowcolor{white} \tt -yPos: double\\
          \hline
          \tt +Point(): Point\\
          \tt +getX(): double\\
          \tt +getY(): double\\
          \tt +setX(x: double): void\\
          \tt +setY(y: double): void\\
          \hline
        \end{tabular}
      \end{minipage}
      &
      <-------------------
      &
      \begin{minipage}{2in}
        \begin{tabular}{|l|}
          \hline
          \rowcolor{orange!20}\multicolumn{1}{|c|}{\bf Circle}\\
          \hline
          \rowcolor{white} \tt -radius: double\\
          \hline
          \tt +Circle(radius: double)\\
          \tt +getRadius(): double\\
          \tt +setRadius(radius: double)\\
          \tt +area(): double\\
          \tt +circumference(): double\\
          \hline
        \end{tabular}
      \end{minipage}
    \end{tabular}
  \end{center}  
  
  {\it\large Refer to Model 2 above as your team develops consensus answers
    to the questions below.}

  \quest{15 min}
    
  \Q What are the attributes and methods of {\tt Circle}, and what
    is their visibility?
    \begin{answer}[0.5in]
      The attributes and methods are:
        Attribute {\tt radius} is private
        Methods {\tt Circle}, {\tt area}, {\tt circumference},
          {\tt getRadius}, and {\tt setRadius} are all public.
    \end{answer}
    
  \Q Based on this model and the previous one, what parts of a
    class are typically private, and what parts are typically public?
    \begin{answer}[0.5in]
      The attributes are typically private and the methods are
      typically public.
    \end{answer}
          
  \Q What does the arrow pointing from the {\tt Circle} class
    diagram to the {\tt Point} class diagram represent?
    \begin{answer}[0.75in]
      It represents the ``is-a'' relationship whereby {\tt Circle} inherits
      the properties of {\tt Point}.
    \end{answer}
    
  \Q The file {\tt activity04b.cpp} contains an implementation of
    the {\tt Point} class.  Write  an\key\\[-2.5mm] implementation of the {\tt
    Circle} class that matches this diagram.
    \begin{answer}[0.8in]
      \scriptsize
      \begin{minipage}{3in}
        \begin{cpplst}
class Circle : public Point {
  public:
    Circle(double radius) {
      this->radius = radius;
    }
    double getRadius() const {
      return this->radius;
    }
    void setRadius(double radius) {
      this->radius = radius;
    }
    double area() const {
      return 3.14159 * radius * radius;
    }
    }double circumference() const {
      return 2 * 3.14159 * radius;
    }
  private:
    double radius;
};
        \end{cpplst}
      \end{minipage}
    \end{answer}