\model{Type Sizes} \\
  Primitive data types in C++ have predefined sizes, which determines 
  the range of values that can be stored in each data type.  Several examples
  are given below.
  
  \begin{center}
    \renewcommand{\arraystretch}{1.8}
    \begin{tabular}{|l|c|c|c|c|}
      \hline
      \cellcolor{orange!20} type & {\tt bool} & {\tt char} & {\tt int} & {\tt double} \\
      \hline
      \cellcolor{orange!20} size & 1 byte & 1 byte & 4 bytes & 8 bytes \\
      \hline
    \end{tabular}
  \end{center}
  
  {\it\large Refer to Model 1 above as your team develops consensus answers
    to the questions below.}
    \par\vskip 10pt
    
  \begin{enumerate}
    \itemsep 20pt

    \Q A single {\bf bit} has only two values (0 or 1), whereas two bits can store four values (00, 01, 10, and 11).
      \par\vskip 20pt
      \begin{enumerate}[(a)]
        \item How many different values can be stored in three bits, and what are they?
          \begin{answer}[0.75in]
            8 different values: 000, 001, 010, 011, 100, 101, 110, and 111
          \end{answer}
        \item What is the smallest binary number in your list in part (a) and what is its base 10 value?
          \begin{answer}[0.75in]
            The smallest number is 000 and its base 10 value is 0.
          \end{answer}
        \item What is the largest binary number in your list in part (a) and what is its base 10 value?
          \begin{answer}[0.75in]
            The smallest number is 111 and its base 10 value is 7.
          \end{answer}
      \end{enumerate}
      
    \Q A {\bf byte} is equivalent to 8 bits.  How many values can be stored in a single byte, and what is the largest
      possible value?  You may wish to use Google as a calculator to solve this problem.
      \begin{answer}[0.75in]
        A byte can hold $2^8 = 256$ values and the largest is 255.
      \end{answer}
      
\newpage

    \Q Complete the following table to determine how many values can be stored in a different number of bytes.  The first
      one is done for you.
      
      \begin{center}
        \renewcommand{\arraystretch}{2}
        \begin{tabular}{|c|c|c|c|}
          \hline
          \rowcolor{orange!20} \# bytes & \# bits & number of values & largest unsigned number possible \\
          \hline
          1 byte & 8 & $2^8 = 256$ & 255 \\
          \hline
          2 bytes & \ifprintanswers 16\fi & \ifprintanswers $2^{16}=65,536$\fi & \ifprintanswers 65,535 \fi\\
          \hline
          4 bytes & \ifprintanswers 32\fi & \ifprintanswers $2^{32}=4,294,967,296$\fi & \ifprintanswers 4,294,967,295\fi\\
          \hline
          8 bytes & \ifprintanswers 64\fi & \ifprintanswers $2^{64}$\fi & \ifprintanswers $2^{64}-1$\fi\\
          \hline
          $x$ bytes & \ifprintanswers $8x$\fi & \ifprintanswers $2^{8x}$\fi & \ifprintanswers $2^{8x}-1$\fi\\
          \hline
        \end{tabular}        
      \end{center}
      
    \Q What is the largest value that a {\tt unsigned short int} variable (of size 2 bytes) can hold?
      \begin{answer}[0.5in]
        An {\tt unsigned short int} can hold $2^16 = 65,536$ values, the largest is 65,535.
      \end{answer}
    
    \Q What happens when you write a C++ assignment statement to set a {\tt unsigned short int}\key\\[-2.5mm] variable equal to one more than this value?
      Try it out using the file `activity04a.cpp`.  Why?
      \begin{answer}[1in]
        \par
        The value wraps around to 0.  That is, the number 65535, represented as 1111111111111111 becomes 0000000000000000
        when we add one to it.
      \end{answer}
      