
  {\bf\large Model 1: Google Directions from KRH to Walmart} \\
  \begin{center}
    \fcolorbox{black}{orange!20}{
    \begin{minipage}{3.5in}
      \begin{enumerate}
        \itemsep -2pt
        \item Head south towards SW 4th Street
        \item Turn left onto SW 4th Street
        \item Travel 499 feet
        \item Turn right onto S. College Avenue
        \item Travel 0.7 miles
        \item Turn left onto Lamperti Lane
        \item Travel 0.2 miles
        \item Continue onto SE Lamperti Street
        \item Travel 469 feet
        \item Turn right into Walmart Parking Lot
        \item Destination will be on the right
      \end{enumerate}
    \end{minipage}
    }
  \end{center}
  \par\vskip 10pt
  
  {\it\large Refer to Model 1 above as your team develops consensus answers
    to the questions below.}
    \par\vskip 10pt
    
  \begin{enumerate}
    \itemsep 20pt
    
    \Q Give at least one assumption that is being made in the
      directions above.
      \begin{answer}[0.75in]
        We are assuming that the individual is driving a car.
      \end{answer}
      \vfill

    \Q List at least two additional instructions that could be
      added to improve on these directions.  Indicate where in the list
      they should be added.
      \begin{answer}[1in]
        \begin{itemize}
          \item Before 1: Get into your car
          \item Between items 3 and 4: Stop at the intersection until
            the light turns green.
          \item Answers will vary{\ldots} 
        \end{itemize}
      \end{answer}
      \vfill
      
\newpage      
      
    \Q An {\it algorithm} is a series of instructions that can be
      repeated over and over with the same results. Based on your
      answers above, give two important things to consider when 
      describing an algorithm.      
      \begin{answer}[1in]
        \begin{itemize}
          \item The context that is assumed
          \item The completeness of the list of instructions
          \item The preciseness of each instruction
          \item etc{\ldots} 
        \end{itemize}
      \end{answer}
      
      
    \Q Think about the process of brushing your teeth.  Write down
      step-by-step instructions\key\\[-3.5mm] (e.g. an algorithm) that
      would allow somebody who has never brushed their teeth before\\
      to successfully accomplish this task.
      \begin{answer}[2.5in]
        Answers will vary.
      \end{answer}
      \vfill
      