
\model{An Object Built Using LEGOs} \\
  \begin{center}
    \fcolorbox{black}{orange!20}{
      \begin{minipage}{5in}
        {\bf Important Instructions}
        \hrule\vskip 5pt
        This model is an object built with LEGO-like blocks. In our
        online environment, we will use the following online LEGO 
        environment.
        \begin{center}
          \href{https://www.mecabricks.com/en/workshop}{https://www.mecabricks.com/en/workshop}
        \end{center}
        It is important that you follow the rules below precisely.
        \begin{enumerate}
          \item Your {\bf driver} should show the video
            ``MecaBricks.mp4'' to the entire group.  This can be found
            in Teams.
          \item Your {\bf manager} should watch the video
            ``ManagerOnly.mp4'' {\bf by themselves}.  Nobody
            else should watch this video.  
          \item Based on the object the manager sees in this video,
            he or she should give instructions to the driver as to
            how to build the object.
          \item Your {\bf team recorder} should write down all
            instructions that are given by the manager.
        \end{enumerate}
        Limit yourself to 5 minutes to complete this task.
      \end{minipage}
    }
  \end{center}
  
{\it\large Refer to Model 2 above as your team develops consensus answers
  to the questions below.}
  \par\vskip 10pt
  
  \Q Give yourself a five minute timmer and then begin constructing
    your object.  Remem\key\\[-3.5mm]ber that the {\bf team manager} is
    the only one who can give instructions and the {\bf team driver}
    and {\bf presenter} may not see the original model.  Work until
    your five minute timer runs out.
    % \begin{answer}[0.3in]
    %   Answers will vary.
    % \end{answer}
    

  \Q How many total instructions were given during your build
    time?
    \begin{answer}[0.75in]
      Answers will vary.
    \end{answer}
    
  \Q Looking through your list of instructions.  Identify several
    that were useful and copy them below.
    \begin{answer}[0.75in]
      Answers will vary.
    \end{answer}
    
  \Q Looking through your list of instructions again, identify
    several that weren't helpful and list them.
    \begin{answer}[0.75in]
      Answers will vary.
    \end{answer}
    
  \Q Describe the types of instructions that work best in
    defining an algorithm.
    \begin{answer}[1in]
      Answers will vary.
    \end{answer}
    
  \Q How was this activity related to computer programming?  How
    is it different?
    \begin{answer}[1in]
      Answers will vary.
    \end{answer}