\model{Your Own Object Built Using LEGOs} \\
    \begin{center}
      \fcolorbox{black}{orange!20}{
        \begin{minipage}{5in}
          \vskip 5pt
          {\bf Important Instructions}
          \hrule\vskip 5pt
            Work together to construct a simple object using the LEGO 
            building program.  Once you are finished, take a screen shot
            of it to show later.
        \end{minipage}
      }
    \end{center}
    \par\vskip 10pt
  
  {\it\large Refer to Model 3 above as your team develops consensus answers
    to the questions below.}
    
      \Q Develop a written algorithm (list of instructions) for
        building your object.
        \begin{answer}[1.5in]
          Answers will vary.
        \end{answer}
        
      \Q Post your algorithm and a list of the number of each size
        of brick used in the general Teams channel.
        
      \Q Pick one of the other team's algorithm to construct their
        object. Reply to their instructions with a screen shot of your
	object.
        
      \Q How well did the other group do at building your object?      
        \begin{answer}[0.75in]
          Answers vary.
        \end{answer}
        
      \Q Suppose the object they built doesn't match your original.
        Describe a scenario in which it would be:
        \begin{enumerate}
          \item the fault of the other team.
            \begin{answer}[0.75in]
              The the other team did not follow the list of
              instructions correctly, it would be their fault.
            \end{answer}
          \item the fault of your team.
            \begin{answer}[0.75in]
              If we did provided an incomplete or imprecise algorithm,
              it would be our fault.
            \end{answer}
        \end{enumerate}
            
      \Q Suppose a program you write does not do what you intended
        it to do.  Describe a\key\\[-2.5mm] scenario in which it would be:
        \begin{enumerate}
          \item the computer's fault.
            \begin{answer}[0.75in]
              If there is a bug in the program that is running your
              code or possibly faulty hardware.
            \end{answer}
          \item your fault as the programmer.
            \begin{answer}[0.75in]
              If the code we gave was inaccurate.
            \end{answer}
        \end{enumerate}
              
      \Q Which of the scenarios in the previous problem do you
        think is most likely?
        \begin{answer}[0.5in]
          It is most likely the programmers fault.
        \end{answer}        