{\bf\large Model 1: A C++ Program} \\[-15pt]
  \begin{center}
    \begin{minipage}{4in}
      \begin{minted}[
        frame=lines,
        framesep=2mm,
        bgcolor=gray!15,
        baselinestretch=1.2,
        linenos,
        firstnumber=4
      ]{cpp}
void printMessage() {
  cout << "Welcome to C++." << endl;
  cout << "Learn the power of functions!" << endl;
}

int main() { 
  cout << "Hello Programmer!" << endl;  
  printMessage();     // function call
}
      \end{minted}
    \end{minipage}
  \end{center}
  \TPMargin{5pt}
  \begin{textblock*}{1.9in}[0,0](4.5in,-1.25in)
    \textblockcolor{white}
    \begin{minipage}{1.75in}
      {\bf Output:} 
      \hrule\vskip 5pt
      Hello Programmer!\\
      Welcome to C++.\\
      Learn the power of functions!
    \end{minipage}
  \end{textblock*}
  
  
  {\it\large Refer to Model 1 above as your team develops consensus answers
    to the questions below.}
    \par\vskip 10pt
    
  \begin{enumerate}
    \itemsep 20pt
    
    \item A {\it function} is a segment of code that encapsulates a
      single task. That is, it combines multiple lines of code into a
      single command.
      \par\vskip 20pt
      
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item Which lines of code belong to the function {\tt printMessage}? \hfill
          \fillin[Lines 4-7][2in]
        \item What other function is defined in this code? \hfill
          \fillin[{\tt main} on lines 9-12][2in]
        \item What does the function {\tt printMessage} do?
          \begin{solution}[0.4in]
            It prints out the two lines ``Welcome to C++'' and ``Learn
            the power of functions!''
          \end{solution}
      \end{enumerate}
      
    \item A {\it function definition} is the segment of code that
      tells the program what to do with the function is executed.  It
      contains a {\it function header} (the first line of the
      definition) and a {\it function body} (the commands that make up
      the function).
      \par\vskip 15pt
      
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item On what line is the function header for {\tt printMessage}? \hfill
          \fillin[Line 4][2in]
        \item On what lines is the function body for {\tt printMessage}?\hfill
          \fillin[Lines 5-6][2in]
      \end{enumerate}
      \vfill
      
\newpage      
    
    \item A {\it function call} is a command that executes the
      function.  Use the code found in {\tt activity11a.cpp} to assist
      you in answering this question.
      \par\vskip 15pt
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item On what line is the function {\tt printMessage} called? \hfill
          \fillin[Line 11][2in]
        \item What happens if you swap lines 10 and 11 in the model above?
          \begin{solution}[0.75in]
            The output would be:\par
            \begin{center}
              \begin{minipage}{3in}
                Welcome to C++\\
                Learn the power of functions!\\
                Hello Programmer!
              \end{minipage}
            \end{center}
          \end{solution}
          \par\vskip -30pt\null
        \item What line of code could you add to make the program
          print the last two lines\key\\[-2.5mm] from the model output twice?  
          Where would you add the code?
          \begin{solution}[1in]
            You could add another function call {\tt printMessage();}
            after line 11.
          \end{solution}
      \end{enumerate}