\model{A C++ Compiler Error}
  \begin{center}
    \begin{tabular}{p{2.5in}p{0.0005in}p{3.4in}}
      \begin{minipage}{2.5in}
        \begin{cpplst}
#include <iostream>
using namespace std;

int main() {
  int varOne = 5;
  if(true) {
    int varTwo = 7;
    cout << varOne << endl;
  }
  cout << varTwo << endl;
}
        \end{cpplst}
      \end{minipage}
      & &
      \begin{minipage}{3.4in}
        {\bf Compiler Error:}
        \scriptsize
        \hrule\vskip 5pt
        \begin{cpplst}
model2.cpp: In function ‘int main()’:
model2.cpp:10:11: error: ‘varTwo’ was not declared in this scope
   10 |   cout << varTwo << endl;
      |           ^~~~~~
        \end{cpplst}
      \end{minipage}
    \end{tabular}
  \end{center}

  {\it\large Refer to Model 2 above as your team develops consensus answers
    to the questions below.}
  
  \Q In your own words, describe what the compiler error shown is all about.
    \begin{answer}[0.5in]
      The variable {\tt varTwo} does  not exist when the {\tt cout} command is given on line 7.
    \end{answer}
  
  \Q On what lines are the following variables defined in the code above?    
    \begin{enumerate}
      \begin{multicols}{2}
        \item The variable {\tt varOne} \hspace{0.025in} \ans[1.25in]{Line 5}
        \item The variable {\tt varTwo} \hfill \ans[1.25in]{Line 7}
      \end{multicols}
    \end{enumerate}
    
  \Q The error message above is triggered by line 10, which comes
    after the variable {\tt varTwo} has been declared.  Why do you
    think the variable {\tt varTwo} is not available on line 10?
    \begin{answer}[0.5in]
      The variable {\tt varTwo} is not visible at line 10 because it
      was declared inside the \cpp{if} block.  So it is
      no longer defined after line 9 when that block ends.
    \end{answer}

  \Q The {\it scope} of a variable is the area of the program in
    which the variable is valid. Variables that have a limited scope
    are called {\it local variables} (unlike global variables, which
    can be accessed anywhere).  In the code in this model:
    \begin{itemize}
      \item The scope of the variable {\tt varOne} is from line 5 to line 11.
      \item The scope of the variable {\tt varTwo} is from line 7 to line 9.
    \end{itemize}
    Based on this information, describe how to find the scope of a
    local variable.
    \begin{answer}[0.5in]
      The scope of a local variable extends from the line on which it
      is defined to the end of the block (code in curly-braces) in
      which it was defined.
    \end{answer}

  \Q The program below defines six different variables different
    variables. Answer the\key\\[-2.5mm] following questions about this code, which can be
    found in {\tt activity14b.cpp}.
    \begin{center}
      \begin{tabular}{p{3.5in}p{2.9in}}
        \begin{minipage}{3.5in}
          \small
          \begin{cpplst}
int a = 0;

void myFunc(int b = 4) {
  int c = 5;
  cout << "Value: " << /* OUTPUT 1 */;
}

int main() {
  int d = 5;
  if (d > 2) {
    int e = 3;
    if (e < 10) {
      int f = 7;
      cout << "Value: " << /* OUTPUT 2 */;
    }
    cout << "Value: " << /* OUTPUT 3 */;
  }
  cout << "Value: " << /* OUTPUT 4 */;
}
          \end{cpplst}
        \end{minipage}
        &
        \begin{minipage}{2.9in}
          \begin{enumerate}
            \item What is the scope of each variable?
              \begin{enumerate}[label=\roman*.]
                \itemsep 10pt
                \item \cpp{int a} -- Lines \ans[0.5in]{1} to \ans[0.5in]{20}
                \item \cpp{int b} -- Lines \ans[0.5in]{3} to \ans[0.5in]{6}
                \item \cpp{int c} -- Lines \ans[0.5in]{4} to \ans[0.5in]{6}
                \item \cpp{int d} -- Lines \ans[0.5in]{9} to \ans[0.5in]{19}
                \item \cpp{int e} -- Lines \ans[0.5in]{11} to \ans[0.5in]{17}
                \item \cpp{int f} -- Lines \ans[0.5in]{13} to \ans[0.5in]{15}
              \end{enumerate}

            \item Identify all global variables.
              \begin{answer}[0.5in]
                Only {\tt a} is a global variable.
              \end{answer}
          \end{enumerate}
        \end{minipage}
      \end{tabular}
    \end{center}

    \begin{enumerate}[label=c)]
      \item What variables could be used in place of each \cpp{/* OUTPUT */}
      comment without causing a compiler error?  List all variables that would work.
      \begin{enumerate}[label=\roman*.]
        \itemsep 10pt
        \begin{multicols}{2}
          \item \cpp{/* OUTPUT 1 */} \hspace{0.0025in} \ans[1.5in]{\tt a, b, c}
          \item \cpp{/* OUTPUT 2 */} \hspace{0.0025in} \ans[1.5in]{\tt a, d, e, f}
          \item \cpp{/* OUTPUT 3 */} \hfill \ans[1.5in]{\tt a, d, e}
          \item \cpp{/* OUTPUT 4 */} \hfill \ans[1.5in]{\tt a, d}
        \end{multicols}
      \end{enumerate}
    \end{enumerate}

  \vskip -30pt
    
  \Q Why is it important to be aware of the scope of a variable?
    \begin{answer}[0.5in]
      Because you can only access that variable within its scope.  So a programmer needs to
      know what that scope will be.
    \end{answer}