\model{Queues - Abstract Data Type}

Note that queues are often described as \textbf{First-In, First-Out (FIFO)}
or \textbf{Last-In, Last-Out (LILO)} (particularly if you are lazy :-) ).

\Q (3 min) Based on the key characteristics of queues that you identified above,
\textbf{list at least 3 key operations} for a queue ADT, and \textbf{rank them} (last column)
by \textbf{importance} (1=high, 5=low).
Review progress with the facilitator before continuing.

\begin{center}
    \begin{tabular}{ |r|p{12cm}|l| }
        \hline
        \rowcolor{lightgray} & \textbf{action or operation} & \textbf{rank} \\
        \hline
        a.                   &                              &               \\
        \hline
        b.                   &                              &               \\
        \hline
        c.                   &                              &               \\
        \hline
        d.                   &                              &               \\
        \hline
    \end{tabular}
\end{center}

\Q (5 min) Start with the most important queue operation above, and define
a method signature including an appropriate name, input parameters, and return types.
You may write the method below, or create an interface file in your IDE (e.g. Code.CS).
Use "T" or "Object" as a generic placeholder for the type of object stored in the queue.
You may include constructors, although Java does not allow interfaces to specify constructors.

\begin{javabox}
public interface IQueue<T> {

    public IQueue<T>(int maxSize); // constructor

    ?

    ?

    ?

    ?

    ?

} // end interface IQueue
\end{javabox}

Review progress with the facilitator before continuing.

\begin{answer}
see Facilitator - Sample Code
NOTE: if students are unfamiliar with generics, use Stack of Strings

REPORT OUT: operations and method signatures, so teams have common framework
Maybe have teams compare their interface to the Java API, Wikipedia,
or their textbook, and summarize any differences, insights, or questions.
\end{answer}
