% Source: https://www.dropbox.com/sh/rl0yyth9g06psva/AADB0Cj4isIX5DAyrspqj8mFa
% File: "CS305 activity 18 hashing.pdf"
% Access: 04-28-2022

% comment out for student version
%\ifdefined\Student\relax\else\def\Teacher{}\fi

\documentclass[12pt]{article}

\title{Activity \#5: Hashing}
\author{Tammy VanDeGrift}
\newcommand{\activityeditor}{Preston Carman}
\newcommand{\activitysource}{\url{https://www.dropbox.com/sh/rl0yyth9g06psva/AADB0Cj4isIX5DAyrspqj8mFa}}
\date{Spring 2022}

\input{../../cspogil.sty}

\begin{document}

  \begin{center}
    \maketitle
    \rolenames
  \end{center}

  \keyquestions{
    \item Model 1, Question \#3
    \item Model 2, Question \#11
    \item Model 2, Question \#12
    \item Model 4, Question \#20
    \item Model 4, Question \#21
  }

  \newpage
  \maketitle

  Recall the List ADT.
  Its operations include insert, find, and delete.
  Earlier, we looked at how find can be implemented using binary search over a sorted list.
  One advantage of binary search is that it only cost $O(log_2N)$ time to execute.
  \par

  One common tradeoff in computer science is the time/space tradeoff.
  In some (maybe many) cases, one can increase runtime speed at the expense of storage space.
  On the flip side, one can often gain efficiency in storage at the expense of running time.
  \par

  We'll look at a way to implement the Dictionary ADT using hash tables.
  As you might guess, we will speed up the dictionary operations at the expense of using more storage space.

  %\rolenames

  \guide{
    \item Explain a hash function
    \item Explain the structure of hash table
    \item Explain how collisions are managed
  }{
    \item Write code that adds, removes, and accesses a hash table
  }{
    No additional notes.
  }

  \input{dictionary_adt.tex}
  \newpage
  \input{hash_functions.tex}
  \newpage
  \input{hash_tables.tex}
  \newpage
  \input{open_address_linear_probing.tex}

\end{document}