\\model{A C++ Program} \\
  \begin{center}
    \begin{minipage}{5.8in}
      \begin{cprlst}[
        frame=lines,
        framesep=2mm,
        bgcolor=gray!15,
        baselinestretch=1.2,
        linenos,
        firstnumber=4
      ]{cpp}
int getSmaller(int num1, int num2) {
  int smaller;
  if (num1 < num2) {
    smaller = num1;
  } else {
    smaller = num2;
  }
  return smaller;
}

int main() {
  int userNum1, userNum2;
  cout << "Enter two numbers separated by a space: ";
  cin >> userNum1 >> userNum2;
  int smallerNum = getSmaller(userNum1, userNum2);
  cout << "The smaller number is " << smallerNum << endl;
}
      \end{cprlst}
    \end{minipage}
  \end{center}
  \TPMargin{5pt}
  \begin{textblock*}{3.1in}[0,0](3.65in,-3.25in)
    \textblockcolor{white}
    \begin{minipage}{2.95in}
      {\bf Output:} 
      \hrule\vskip 5pt
      Enter two numbers separated by a space: 52 36\\
      The smaller number is 36
    \end{minipage}
  \end{textblock*}
  
  
  {\it\large Refer to Model 1 above as your team develops consensus answers
    to the questions below.}
    \par\vskip 10pt
    
  \begin{enumerate}
    \itemsep 20pt

    \Q What does the function defined on lines 4-12 do?
      % \ifprintanswers\vskip -10pt\fi
      \begin{answer}[0.25in]
        It returns the smaller of the two integer arguments passed to it.
      \end{answer}
      % \ifprintanswers\vskip -35pt\null\fi
      
    \Q So far you have created `void` functions which do not send any
      information back to the calling code. A {\it value-returning} function
      does send information of a particular type back to the calling code.
      % \par\ifprintanswers\vskip 10pt\else\vskip 20pt\fi
      
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item What type of information does the function {\tt getSmaller} return? \hfill
          \ans[1.8in]{An integer}
        \item On what line of code is the function call to {\tt getSmaller}? \hfill
          \ans[1.8in]{Line 15}
        \item On what line does the function {\tt getSmaller} send back a value? \hfill
          \ans[1.8in]{Line 8]
      \end{enumerate}

\newpage      

    \Q In a {\it void function} the {\it function call} is on a line by itself.
      Why is the function call in this model on the right-hand-side of an
      assignment statement?
      \begin{answer}[0.5in]
        Because it returns a value that is being assigned to the variable {\tt
        smallerNum}.
      \end{answer}      
      
    \Q If you wanted to alter this function to select and return the
      smaller of two {\tt  double} values,\key\\[-2.5mm] what changes would you
      need to make?
      \begin{answer}[1in]
        You need to change the \cpp{int} type to a
        \cpp{double} in the following places.
        \begin{itemize}
          \begin{multicols}{2}
            \item In the three instances on line 1
            \item In the one instance on line 2
          \end{multicols}
        \end{itemize}
      \end{answer}