{\bf\large Model 2: A C++ Function} \\[-20pt]
  \begin{center}
    \begin{minipage}{4.5in}
      \begin{minted}[
        frame=lines,
        framesep=2mm,
        bgcolor=gray!15,
        baselinestretch=1.2,
        linenos
      ]{cpp}
void getHypotenuse(double a, double b) {
  double square = pow(a,2) + pow(b,2);
  double squareRoot = sqrt(square);
  cout << "The hypotenuse length is " << squareRoot << endl;
}
      \end{minted}
    \end{minipage}
  \end{center}


  {\it\large Refer to Model 2 above as your team develops consensus answers
    to the questions below.}

    \item What does this function do?
      \ifprintanswers\vskip -20pt\null\fi
      \begin{solution}[0.35in]
        It solves for the length of the hypotenuse of a right triangle given
        the length of the two legs and prints it out.
      \end{solution}
      \ifprintanswers\vskip -35pt\null\fi
      
    \item Is this a {\it void function} or a {\it value-returning} function?
      \hfill\fillin[void][2in]

    \item Suppose you wanted to turn this into a value-returning function
      that returns the hypotenuse length.
      \par\vskip 15pt
    
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item How would you change line 1 in the model? \hfill
          \fillin[\mintinline{cpp}|double getHypotenuse(double a, double b)|][3in]
        \item What command would you add to the end? \hfill
          \fillin[\mintinline{cpp}|return squareRoot;|][3in]
        \item What line would you remove and why? \hfill
          \fillin[Line 4 -- function doesn't produce output][3in]
      \end{enumerate}
      
    \item What is the difference between using {\tt cout} in a function and using
      {\tt return} in a function?
      \begin{solution}[0.5in]
        Using {\tt cout} prints values out to the screen while using {\tt return}
        sends the value back to the caller, where it can decide what to do with it.
      \end{solution}
    
\newpage
    \null\vskip -60pt\null
    \item Below is the framework for a program that drills students on addition
      problems.\key\\[-2.5mm]  In particular, the program should do the following:
      \begin{itemize}
        \item Display five addition problems, one at a time, and let the student answer each
        \item Print the correct answer if the user enters an incorrect answer
        \item Print a congratulatory message if the student's answer is correct
        \item Keep track of the number of problems the student answers correctly
        \item Print a special message if the user gets all five problems right
      \end{itemize}
      Fill in the missing code to make this program function
      as described.  The code is in {\tt activity12b.cpp}.
      \vskip -30pt\null
    
      \begin{center}
        \begin{tabular}{p{2.75in}p{0.1in}p{2.8in}}
          \begin{minipage}{2.75in}
            \begin{minted}[
              frame=lines,
              framesep=2mm,
              bgcolor=gray!15,
              baselinestretch=1.2,
              linenos,
              firstnumber=5
            ]{cpp}
// Print celebratory rocket

/* ANSWER A */ printRocket() {
  cout << "Blast-off!" << endl;
  cout << "  ^"    << endl;
  cout << " /*\\"  << endl;
  cout << "/***\\" << endl;
  cout << "|***|"  << endl;
  cout << "|***|"  << endl;
  cout << "|#|#|"  << endl;
  /* ANSWER B */
}

// give problem and check answer
bool giveProblem(/* ANSWER C */) {
  int studentAns;
  int correctAns = num1+num2;
  cout << num1 << "+" << num2 << "=";
  cin >> studentAns;
  /* ANSWER D */
}
            \end{minted}
          \end{minipage}
          & &
          \begin{minipage}{2.8in}
            \begin{minted}[
              frame=lines,
              framesep=2mm,
              bgcolor=gray!15,
              baselinestretch=1.2,
              linenos,
              firstnumber=27
            ]{cpp}          
int main() {
  srand(time(0));  // seed random num
  int numCorrect = 0;
  for(/* ANSWER E */) {
    int num1 = rand() % 10 + 1;
    int num2 = rand() % 10 + 1;
    if (/* ANSWER F */) {
      cout << "Correct!" << endl;
      numCorrect++;
    } else {
      cout << "Incorrect! It is "
           << (num1 + num2) << endl;
    }
  }
  if( /* ANSWER G */ ) {
    /* ANSWER H */
  } else {
    cout << "You got " << numCorrect
         << " correct." << endl;
  }
}
            \end{minted}
          \end{minipage}
        \end{tabular}
      \end{center}
      
      \begin{enumerate}[A.]
        \begin{multicols}{2}
          \item Line 7: The type of {\tt printRocket}:\par
            \begin{minipage}{2.75in}
              \begin{solution}[0.55in]
                {\tt void}
              \end{solution}
            \end{minipage}
          \item Line 15: A {\tt return} statement:\par
            \begin{minipage}{2.75in}
              \begin{solution}[0.55in]
                {\tt return} or empty
              \end{solution}
            \end{minipage}
          \item Line 19: Parameters for {\tt giveProblem}:\par
            \begin{minipage}{2.75in}
              \begin{solution}[0.55in]
                \mintinline{cpp}|int num1, int num2|
              \end{solution}
            \end{minipage}
          \item Line 24: A {\tt return} statement:\par
            \begin{minipage}{2.75in}
              \begin{solution}[0.55in]
                \small
                \mintinline{cpp}|return studentAns==correctAns|
              \end{solution}
            \end{minipage}
          \item Line 30: Setup for {\tt for} loop:\par
            \begin{minipage}{2.75in}
              \begin{solution}[0.55in]
                \mintinline{cpp}|int i=0; i<5; i++|
              \end{solution}
            \end{minipage}
          \item Line 33: Function call in {\tt if} condition:\par
            \begin{minipage}{2.75in}
              \begin{solution}[0.55in]
                \mintinline{cpp}|giveProblem(num1,num2)|
              \end{solution}
            \end{minipage}
          \item Line 41: Condition for {\tt if} statement:\par
            \begin{minipage}{2.75in}
              \begin{solution}[0.55in]
                \mintinline{cpp}|numCorrect==5|
              \end{solution}
            \end{minipage}
          \item Line 42: Command if all 5 correct:\par
            \begin{minipage}{2.75in}
              \begin{solution}[0.55in]
                \mintinline{cpp}|printRocket();|
              \end{solution}
            \end{minipage}                      
        \end{multicols}
      \end{enumerate}