{\bf\large Model 3: Program Output and the {\tt main} Function} \\[-10pt]

  \begin{center}
    \begin{tabular}{p{3in}p{2.7in}}
      \begin{minipage}{3in}
        \small
        \begin{minted}[
          frame=lines,
          framesep=2mm,
          bgcolor=gray!15,
          baselinestretch=1.2,
          linenos,
          firstnumber=7
        ]{cpp}
int main() {
  int userNum,compNum;
  char tryAgain;
  srand(time(0));
  do {
    do {
      cout << "Enter a number from 1 to 5: ";
      cin >> userNum;
      if (userNum < 1 || userNum > 5) {
        cout << "Invalid Number!" << endl;
      }
    } while (userNum < 1 || userNum > 5);
    compNum = rand() % 5 + 1;
    cout << "Computer number: " 
         << compNum << endl;
    cout << "Your number: " 
         << userNum << endl;
    cout << getMessage(userNum,compNum);
    cout << "Try again (y/n)? ";
    cin >> tryAgain;    
  } while (tryAgain=='y');
}
        \end{minted}
      \end{minipage}
      &
      \fbox{\begin{minipage}{2.4in}
        \small
        {\bf Output:} 
        \hrule\vskip 5pt\tt
        Enter a number from 1 to 5: 7\\
        Invalid Number!\\
        Enter a number from 1 to 5: 3\\
        Computer number: 3\\
        Your number: 3\\
        Congratulations! You guessed it.\\
        Try again (y/n)? y\\
        \\
        Enter a number from 1 to 5: 3\\
        Computer number: 4\\
        Your number: 3\\
        I'm sorry, your number is smaller.\\
        Try again (y/n)? y\\
        \\    
        Enter a number from 1 to 5: 3\\
        Computer number: 1\\
        Your number: 3\\
        I'm sorry, your number is larger.\\
        Try again (y/n)? n\\
      \end{minipage}}
    \end{tabular}
  \end{center}
      
  {\it\large Refer to Model 3 above as your team develops consensus answers
    to the questions below.}

    \item There is one user-defined function that is missing from this program.
      \par\vskip 15pt
      
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item What is the name of the missing function? \hfill
          \fillin[\tt getMessage][3in]
        \item Is the function {\tt void} or value-returning? \hfill
          \fillin[value-returning][3in]
        \item What are the type(s) of its parameters?\hfill
          \fillin[It has two integer parameters][3in]
        \item Write the header for the function. \hfill
          \fillin[\mintinline{cpp}|string getMessage(int uNum, int cNum)|][3in]
      \end{enumerate}
      \par\vskip -40pt\null
      
    \item Does the missing function contain any {\tt cout} statements?
      Explain your reasoning.\key
      \ifprintanswers\vskip -20pt\null\fi
      \begin{solution}[0.5in]
        No.  It returns the value to print out, but the {\tt cout}
        happens in the {\tt main} function, not in the missing function.
      \end{solution}
      
    \item Suppose line 24 in the model was changed to just
      \mintinline{cpp}|getMessage(userNum,compNum);|.  How would this
      change your answers to questions 10 and 11 above?
      \ifprintanswers\vskip -20pt\null\fi
      \begin{solution}[0.5in]
        The function now produces the output and would have a {\tt
        void} return type.
      \end{solution}
           
\newpage

    \item Now write the function definition assuming that the function header
      is as shown below.
      \begin{center}
        \mintinline{cpp}|string getMessage(int userNum, int compNum)|
      \end{center}
      \begin{solution}[2.25in]
        \scriptsize\vskip -35pt\null
        \begin{center}
          \begin{minipage}{3.5in}
            \begin{minted}[
              frame=lines,
              framesep=2mm,
              bgcolor=gray!15,
              baselinestretch=1.2,
              linenos
            ]{cpp}
string getMessage(int userNum,int compNum) {
  string message;
  if (userNum < compNum) {
    message = "I'm sorry, your number is smaller.\n";
  } else if (userNum > compNum) {
    message = "I'm sorry, your number is larger.\n";
  } else {
    message = "Congratulations!  You picked the number.\n";
  }
  return message;
}
            \end{minted}
          \end{minipage}
        \end{center}\vskip -20pt\null
      \end{solution}          
  
    \item Write a different version of this same function assuming that
      line 24 in the model was changed to just \mintinline{cpp}|getMessage(userNum,compNum);| 
      and using the following function header.
      \begin{center}
        \mintinline{cpp}|void getMessage(int userNum, int compNum)|
      \end{center}
      \begin{solution}[2.25in]
        \scriptsize\vskip -35pt\null
        \begin{center}
          \begin{minipage}{3.5in}
            \begin{minted}[
              frame=lines,
              framesep=2mm,
              bgcolor=gray!15,
              baselinestretch=1.2,
              linenos
            ]{cpp}
void getMessage(int userNum,int compNum) {
  if (userNum < compNum) {
    cout << "I'm sorry, your number is smaller." << endl;
  } else if (userNum > compNum) {
    cout << "I'm sorry, your number is larger." << endl;
  } else {
    cout << "Congratulations!  You picked the number." << endl;
  }
}
            \end{minted}
          \end{minipage}
        \end{center}\vskip -20pt\null
      \end{solution}          
