{\bf\large Model 1: A C++ Programs} \\[-15pt]
  \begin{center}
    \begin{minipage}{2.5in}
      \begin{minted}[
        frame=lines,
        framesep=2mm,
        bgcolor=gray!15,
        baselinestretch=1.2,
        linenos,
        firstnumber=6
      ]{cpp}
  string name;
  cout << "What is your name? ";
  cin >> name;
  for (int i=0; i<5; i++) {
    for (int j=0; j<3; j++) {
      cout << name << " ";
    }
    cout << endl;
  }
      \end{minted}
    \end{minipage}
  \end{center}
  \TPMargin{5pt}
  
  
  {\it\large Refer to Model 1 above as your team develops consensus answers
    to the questions below.}
    \par\vskip 10pt
    
  \begin{enumerate}
    \itemsep 20pt
    
    \item What does this program display?  Try to determine this
      without running it first, then check your work against
      the output of the program in {\tt activity09a.cpp}.
      \begin{solution}[0.75in]
        \par
        The program prints out a 3 x 5 grid of the person's name.
      \end{solution}
      
    \item Answer the following questions regarding the      
      \mintinline{cpp}|for| loops in this code snippet.
      \par\vskip 20pt
      
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item How many \mintinline{cpp}|for| loops are in this code?: \hfill
          \fillin[There are two][2.5in]
        \item Does one loop completely finish before the next begins?  \hfill
          \fillin[No.  One loop is inside the other][2.5in]
        \item What do you call this arrangement of loops?  \hfill
          \fillin[These are nested loops][2.5in]
      \end{enumerate}
    
    \item How many times does each {\tt cout} statement in this model
      execute?
      \par\vskip 20pt
      
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item The {\tt cout} on line 7 of the model:\hfill
          \fillin[Executes once][2.5in]
        \item The {\tt cout} on line 11 of the model: \hfill
          \fillin[Executes $5\times 3 = 15$ times][2.5in]
        \item The {\tt cout} on line 13 of the model: \hfill
          \fillin[Executes five times][2.5in]
      \end{enumerate}
      
\newpage

    \item A loop that appears within another loop is called a {\it
      nested loop}.  We can refer to the two loops as the {\it outer
      loop} and the {\it inner loop}.
      \par\vskip 20pt
      
      \begin{enumerate}[(a)]
        \itemsep 15pt
        \item On what line number in the model does the outer loop start?\hfill
          \fillin[Line 4][2in]
        \item On what line number in the model does the inner loop start? \hfill
          \fillin[Line 5][2in]
        \item On what line number does the inner loop in the model end?\hfill
          \fillin[Line 7][2in]
        \item On what line number does the outer loop in the model end?\hfill
          \fillin[Line 9][2in]
      \end{enumerate}
      \par\vskip -35pt\null
                
    \item What does each of the loops in the model do?\key\\[-2.5mm]
      \begin{enumerate}[(a)]
        \item What does the inner loop do?
          \begin{solution}[0.5in]
            The inner loop prints out a name 3 times with a space
            after each one.
          \end{solution}
        \item What does the outer loop do?
          \begin{solution}[0.5in]
            The outer loop repeats the inner loop 5 times and prints
            an {\tt endl} after each one.
          \end{solution}
      \end{enumerate}
      \par\vskip 10pt
