\model{Another C++ Program} \\
  % \ifprintanswers\vskip -40pt\null\fi
  \begin{center}
    \small
    \begin{minipage}{5.5in}
      \begin{cprlst}[
        frame=lines,
        framesep=2mm,
        bgcolor=gray!15,
        baselinestretch=1.2,
        linenos
      ]{cpp}
#include <iostream>
using namespace std;

int main() {
  int numCredits = 194;
  double majorGPA = 2.9;
  double overallGPA = 2.1;
  if ( /* missing Boolean expression */ ) {
    cout << "Congratulations!" << endl;
    cout << "You seem to meet the criteria for graduation." << endl;
  } else {
    cout << "Sorry!" << endl;
    cout << "You do not meet all the criteria for graduation." << endl;
  }
}      
      \end{cprlst}
    \end{minipage}
  \end{center}
  \TPMargin{5pt}
  % \ifprintanswers\vskip -20pt\null\fi
  

  {\it\large Refer to Model 2 above as your team develops consensus answers
    to the questions below.}
    \par\vskip 10pt

    \Q In order to graduate from WWU with a Bachelor's degree, students must have
      earned at least 192 credits, have a GPA of at least 2.0 in their major, and have an
      overall GPA of at least 2.0 (among other things).  Which of the following Boolean
      expressions should be used on line 8 of this model to test if a student meets these
      graduation criteria?
      \par\vskip 10pt
      \begin{checkboxes}
        \choice \cpp{numCredits >= 192 || majorGPA >= 2.0 || overallGPA >= 2.0}
        \choice \cpp{numCredits > 192 && majorGPA > 2.0 && overallGPA > 2.0}
        \correctchoice \cpp{numCredits > 191 && majorGPA >= 2.0 && overallGPA >= 2.0}
        \correctchoice \cpp{numCredits >= 192 && majorGPA >= 2.0 && overallGPA >= 2.0}
      \end{checkboxes}
      \par\vskip -30pt\null

    \Q Add the Boolean expression you chose above to the program in {\tt activity06b.cpp}. Create \key\\[-2.5mm]
      test data to check all eight ($2\times 2\times 2$) different combinations for
      the sub-expressions of the Boolean expression.  Then run each of those test cases and verify that 
      the program passes the test. 
      \par\vskip 15pt
      \begin{center}
        \renewcommand{\arraystretch}{1.8}
        \begin{tabular}{|c|c|c|c|c|c|}
          \hline
            \rowcolor{orange!20} Test Case & {\tt numCredits} & {\tt majorGPA} & {\tt overallGPA} & Expected (graduate/don't) & Passed \\
          \hline
            1 & \ifprintanswers 196\fi & \ifprintanswers 3.6\fi & \ifprintanswers 3.2\fi & \ifprintanswers graduate\fi & \\
          \hline
            2 & \ifprintanswers 196\fi & \ifprintanswers 3.6\fi & \ifprintanswers 1.8\fi & \ifprintanswers don't\fi & \\
          \hline
            3 & \ifprintanswers 196\fi & \ifprintanswers 1.9\fi & \ifprintanswers 3.2\fi & \ifprintanswers don't\fi & \\
          \hline
            4 & \ifprintanswers 196\fi & \ifprintanswers 1.7\fi & \ifprintanswers 1.9\fi & \ifprintanswers don't\fi & \\
          \hline
            5 & \ifprintanswers 188\fi & \ifprintanswers 3.6\fi & \ifprintanswers 3.2\fi & \ifprintanswers don't\fi & \\
          \hline
            6 & \ifprintanswers 184\fi & \ifprintanswers 3.2\fi & \ifprintanswers 1.8\fi & \ifprintanswers don't\fi & \\
          \hline
            7 & \ifprintanswers 190\fi & \ifprintanswers 1.9\fi & \ifprintanswers 3.2\fi & \ifprintanswers don't\fi & \\
          \hline
            8 & \ifprintanswers  53\fi & \ifprintanswers 1.6\fi & \ifprintanswers 1.9\fi & \ifprintanswers don't\fi & \\
          \hline
        \end{tabular}
      \end{center}
      
    \Q A {\it edge case test} is a test of a natural edges or boundary of the program.  An example of a natural boundary
      in this program is where the {\tt majorGPA} is exactly 2.0, since this is a division line in determining if somebody can
      graduate.  Give at least two other edge cases that could be tested.
      \begin{answer}[1in]
        \par
        We could test where {\tt overallGPA} is exactly 2.0 and where {\tt numCredits} is exactly 192.  Additional boundary
        conditions might include the limits of an integer range for {\tt numCredits}, the division line between positive and
        negative values, etc.
      \end{answer}