\model{Representing Graphs}

  \quest{15 min}

  Now, to the implementation part of graphs.
  There are two standard ways to represent a graph in code.
  One representation uses an adjacency matrix.
  The other representation uses adjacency lists.

  \par\vskip 10pt

  \textbf{Adjacency Matrix}

  \par\vskip 10pt

  An adjacency matrix M is a $|V| x |V|$ (2D array) of integers.
  You can number the vertices 0 to $|V|-1$ (or have a mapping of vertex names to numbers 0 to $|V|-1$).
  If there is no edge from vertex x and vertex y, then $M[x][y]=0$ (note that book uses infinity; either value works as long as the implementation knows how to treat the value representing ``no edge'').
  If there is an edge from vertex x to y with cost C, then $M[x][y] = C$.

  \par\vskip 10pt

  If the graph is directed, $M[x][y]$ does not need to equal $M[y][x]$.
  If the graph is undirected, $M[x][y] = M[y][x]$.
  If the graph edges have no costs, then M contains just 0's and 1's (and can store bits instead of ints).

  \par\vskip 10pt

  \textbf{Adjacency List}

  \par\vskip 10pt

  An adjacency list L is a list (linked list or array) of vertices.
  Each vertex stores a list of the vertices that are adjacent to it.
  If the edges have costs, then the adjacent vertices are stored as (V, C) pairs where V is the vertex and C is the cost.

  \par\vskip 10pt

  Here is the adjacency matrix for the first graph in this handout:

  \begin{tabular}{ c | c c c c c }
      & A & B & C & D & E \\ \hline
    a & 0 & 0 & 0 & 0 & 0 \\
    b & 0 & 0 & 1 & 0 & 2 \\
    c & 0 & 3 & 2 & 0 & 0 \\
    d & 0 & 4 & 5 & 0 & 0 \\
    e & 6 & 0 & 0 & 7 & 1 \\
  \end{tabular}

  \par\vskip 10pt

  Here is the adjacency list for the first graph in this handout:

  \begin{tabular}{ l }
    a $-> \{\}$                       \\
    b $-> \{(c, 1), (e, 2)\}$         \\
    c $-> \{(b, 3), (c, 2)\}$         \\
    d $-> \{(b, 4), (c, 5)\}$         \\
    e $-> \{(a, 6), (d, 7), (e, 1)\}$ \\
    \end{tabular}

  \newpage

  \Q Here is the adjacency matrix for an undirected graph.
    Draw the circles and edges\key\\[-2.5mm] (links) below.

    \par\vskip 10pt

    \begin{tabular}{ c | c c c c c }
        & a & b & c & d \\
      a & 0 & 2 & 1 & 0 \\
      b & 2 & 0 & 3 & 1 \\
      c & 1 & 3 & 0 & 4 \\
      d & 0 & 1 & 4 & 0 \\
    \end{tabular}

  \vskip -20pt

  \Q Here is the adjacency list for an undirected unweighted graph.
    Draw the circles and\key\\[-2.5mm] edges (links) below.
    \par\vskip 10pt
    \begin{tabular}{ l }
      $a -> \{c, e\} $      \\
      $b -> \{c, d\} $      \\
      $c -> \{a, b, d, e\}$ \\
      $d -> \{b, c, e\} $   \\
      $e -> \{a, c, d\} $   \\
    \end{tabular}

  \vskip -20pt

  \Q What is the maximum number of edges an undirected graph with 5 vertices can\key\\[-2.5mm] have?
  \begin{answer}[0.3in]
    It can have 10 edges
  \end{answer}

  \Q What is the maximum number of edges a directed graph with 5 vertices can have?
  \begin{answer}[0.3in]
    It can have 20 edges
  \end{answer}

  A \textit{sparse} graph is a graph that has few edges compared to the number of vertices in the graph.

  \Q Draw a sparse graph here:
    \begin{answer}[1in]
      Drawings will vary.
    \end{answer}

  A \textit{dense} graph is a graph that has lots of edges compared to the number of vertices in the graph.

  \Q Draw a dense graph here:
    \begin{answer}[1in]
      Drawings will vary.
    \end{answer}

  \Q Suppose you know your graph is sparse. Would you use the adjacency matrix or adjacency list representation?
    \ans[.25in]{} matrix \ans[.25in]{\checkmark} list

  \Q Suppose you know your graph is dense. Would you use the adjacency matrix or adjacency list
    representation?
    \ans[.25in]{\checkmark} matrix \ans[.25in]{} list

  \Q Suppose you want to determine if node a is connected to node c in a graph.
    Node a is mapped to position 0 in the matrix and list representations.
    Node c is mapped to position 2 in the matrix and list representations.

    \par\vskip 10pt

    How long (worst-case) does it take to determine if a is connected to c using the matrix representation?
    O(\ans[.25in]{1})

    \par\vskip 10pt

    How long (worst-case) does it take to determine if a is connected to c using the adjacency list representation?
    Assume the list of adjacent nodes is not in order. O(\ans[.25in]{V})

    \par\vskip 10pt

  \Q What questions does your group have about graphs?
    \begin{answer}[1in]
      Answers will vary.
    \end{answer}